\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-04-18 doc/sw-system.tex
Amended reference to magnification cut in Paper 2 #105

\new{At this point, the distribution of lens and source properties are quite
realistic. At this point, we chose to make several cuts, to reject sims that
were likely to be difficult to spot. While this ensured the educational value
of the sims when giving feedback, it meant that we should only {\it expect} to
detect real lens candidates that also pass these cuts. Any real lenses
candidates we find with properties outside the ranges of the sims may in some
sense be considered bonuses, a product of the {\it imagination} of the crowd
in extrapolating their understanding of gravitational lenses into a regime
where they have not seen any before. In the CFHTLS project, the most important
selection cuts were to only keep sims with a)  second brightest image brighter
that $i = 23$ and b) magnification greater than 20 (\PaperTwo, Table 1).}

>>>>

\new{At this point, the distribution of lens and source properties are quite
realistic. At this point, we chose to make several cuts, to reject sims that
were likely to be difficult to spot. While this ensured the educational value
of the sims when giving feedback, it meant that we should only {\it expect} to
detect real lens candidates that also pass these cuts. Any real lenses
candidates we find with properties outside the ranges of the sims may in some
sense be considered bonuses, a product of the {\it imagination} of the crowd
in extrapolating their understanding of gravitational lenses into a regime
where they have not seen any before. In the CFHTLS project, the most important
selection cuts were to only keep sims with a)  second brightest image brighter
that $i = 23$ and b) total combined image magnitude brighter than 19--20
(\PaperTwo, Table 1).} The combination of these two cuts results in a sample of
visible lensed image configurations.
